Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/compilation.tex
space savings

At a first cut, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly. The PGIR captures this notion of choice precisely. For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$. However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case. This remains true despite any failures that might have occurred in the network. Thus $D$ can safely prefer $X$ and $Y$ equally.

@@

\begin{figure}[t!]
%% \begin{lstlisting}[frame=single, mathescape=true]
%% $\Router{A}$
%%   Match $\PEER=C, \COMM=(3,2)$
%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
%% $\Router{B}$
%%   Match $\PEER = C, \COMM = (-,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%%   Match $\PEER = C, \COMM = (3,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%% $\Router{C}$
%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
%%   Match $\PEER = D, \COMM = (2,2)$
%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
%% $\Router{D}$
%%   Match $\REGEX{X + Y}$
%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
%% $\Router{E}$
%%   Match $\REGEX{Z}$
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
%% \end{lstlisting}
\begin{code}
\Router{A}
  Match \PEER=C, \COMM=(3,2)
    Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
\Router{B}
  Match \PEER = C, \COMM = (-,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
  Match \PEER = C, \COMM = (3,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
\Router{C}
  Match[LP=99] \PEER = E, \COMM = (-,2) 
    Export \COMM \Arrow (-,2), \PEER \Arrow B
  Match \PEER = D, \COMM = (2,2)
    Export \COMM \Arrow (3,2), \PEER \Arrow A,B
\Router{D}
  Match \REGEX{X + Y}
    Export \COMM \Arrow (2,2), \PEER \Arrow C
\Router{E}
  Match \REGEX{Z}
    Export \COMM \Arrow (-,2), \PEER \Arrow C
\end{code}\vspace{-1cm}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}

@@

Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes. Instead, it translates matches from external ASes into a BGP regular expression filter. For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$. In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters. Any unknown AS topology is modelled as a special node in the product graph that generates a filter to match any sequence of ASes.

Finally, in our example, the external AS $W$ should prefer our internal router $A$ over $B$. In general, it is not possible to reliably control traffic entering the network beyond certain special cases. In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$. Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic. The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology. 
%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default. Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
Figure~\ref{fig:config} shows the full configuration from the compilation example.

@@

A distributed BGP configuration produced by \sysname is \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.

@@

A distributed BGP configuration produced by \sysname is \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.

@@

The internal routers in a distributed BGP configuration produced by \sysname will be stable. 

>>>>

At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly. The PGIR captures this notion of choice precisely. For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$. However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case. This remains true despite any failures that might have occurred in the network. Thus $D$ can safely prefer $X$ and $Y$ equally.

@@

\begin{figure}[t!]
%% \begin{lstlisting}[frame=single, mathescape=true]
%% $\Router{A}$
%%   Match $\PEER=C, \COMM=(3,2)$
%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
%% $\Router{B}$
%%   Match $\PEER = C, \COMM = (-,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%%   Match $\PEER = C, \COMM = (3,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%% $\Router{C}$
%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
%%   Match $\PEER = D, \COMM = (2,2)$
%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
%% $\Router{D}$
%%   Match $\REGEX{X + Y}$
%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
%% $\Router{E}$
%%   Match $\REGEX{Z}$
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
%% \end{lstlisting}
\begin{code}
\Router{A}
  Match \PEER=C, \COMM=(3,2)
    Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
\Router{B}
  Match \PEER = C, \COMM = (-,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
  Match \PEER = C, \COMM = (3,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
\Router{C}
  Match[LP=99] \PEER = E, \COMM = (-,2) 
    Export \COMM \Arrow (-,2), \PEER \Arrow B
  Match \PEER = D, \COMM = (2,2)
    Export \COMM \Arrow (3,2), \PEER \Arrow A,B
\Router{D}
  Match \REGEX{X + Y}
    Export \COMM \Arrow (2,2), \PEER \Arrow C
\Router{E}
  Match \REGEX{Z}
    Export \COMM \Arrow (-,2), \PEER \Arrow C
\end{code}\vspace{-.5cm}
\label{fig:abgp-config}
\caption{Abstract BGP router configurations.}
\end{figure}

@@

Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes. Instead, it translates matches from external ASes into a BGP regular expression filter. For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$. In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters. The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.

Finally, in our example, the external AS $W$ should prefer our internal router $A$ over $B$. In general, it is not possible to reliably control traffic entering the network beyond certain special cases. In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$. Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic. The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology. 
%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default. Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.

@@

BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.

@@

BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.

@@

BGP configurations for internal routers produced by \sysname will be stable. 
